---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# checkenv

<!-- badges: start -->
[![R-CMD-check](https://github.com/briandconnelly/checkenv/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/briandconnelly/checkenv/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

checkenv is a collection of lightweight functions that can be used to determine the computing environment in which your code is running.
This includes Continuous Integration (CI) environments, containers, different operating systems, and more.

Similar or identical functions already exist.
However, most of these functions exist within highly specialized packages, so using several of them can quickly create a lot of dependencies for your own projects.
The goal of checkenv is to provide a unified collection of checks that can be used to better understand the environments in which your code is running.


## Installation

If you’d like to try out the development version of checkenv, you can
install directly from GitHub:

``` r
# install.packages("remotes")
remotes::install_github("briandconnelly/checkenv")
```

## Some Examples

### Am I online?

```{r}
library(checkenv)

is_online()
```

**Alternatives:** [`curl::has_internet()`](https://jeroen.cran.dev/curl/reference/nslookup.html) (used by checkenv), [`testthat::skip_if_offline()`](https://testthat.r-lib.org/reference/skip.html), [`pingr::is_online()`](https://github.com/r-lib/pingr) 


### Am I using RStudio?

```{r}
using_rstudio()
```


### Am I using macOS? On an Intel Mac?

```{r}
using_macos()
```

```{r}
using_macos() && using_x86_cpu()
```


### Are we running in a Docker container?

```{r}
using_docker_container()
```


### Are we using a continuous integration service? GitHub Actions?

```{r}
using_ci()

using_github_actions()
```

**Alternatives:** [`testthat::skip_on_ci()`](https://testthat.r-lib.org/reference/skip.html) (and `on_ci()`), [`testthat::skip_on_travis()`](https://testthat.r-lib.org/reference/skip.html), [`testthat::skip_on_appveyor()`](https://testthat.r-lib.org/reference/skip.html) 
