---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ami

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/briandconnelly/ami/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/briandconnelly/ami/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/briandconnelly/ami/branch/main/graph/badge.svg)](https://app.codecov.io/gh/briandconnelly/ami?branch=main)
<!-- badges: end -->

ami is a collection of lightweight functions that can be used to determine the computing environment in which your code is running.
This includes Continuous Integration (CI) environments, containers, different operating systems, and more.

Similar or identical functions already exist.
However, most of these functions exist within highly specialized packages, so using several of them can quickly create a lot of dependencies for your own projects.
The goal of ami is to provide a unified collection of checks that can be used to better understand the environments in which your code is running.


## Installation

If you’d like to try out the development version of ami, you can
install directly from GitHub:

``` r
# install.packages("remotes")
remotes::install_github("briandconnelly/ami")
```

## Some Examples

### Am I online?

```{r}
ami::online()
```

*Alternatives:* [`curl::has_internet()`](https://jeroen.cran.dev/curl/reference/nslookup.html) (used by ami), [`testthat::skip_if_offline()`](https://testthat.r-lib.org/reference/skip.html), [`pingr::is_online()`](https://github.com/r-lib/pingr) 


### Am I using RStudio?

```{r}
ami::using_rstudio()
```

*Alternatives:* [`rstudioapi::isAvailable()`](https://rstudio.github.io/rstudioapi/reference/isAvailable.html)

### Am I using macOS? On an Intel Mac?

```{r}
ami::using_macos()
```

```{r}
ami::using_macos() && ami::using_x86_cpu()
```


### Are we running in a Docker container?

```{r}
ami::using_docker_container()
```


### Are we using a continuous integration service? GitHub Actions?

```{r}
ami::using_ci()

ami::using_github_actions()
```

*Alternatives:* [`testthat::skip_on_ci()`](https://testthat.r-lib.org/reference/skip.html) (and `on_ci()`), [`testthat::skip_on_travis()`](https://testthat.r-lib.org/reference/skip.html), [`testthat::skip_on_appveyor()`](https://testthat.r-lib.org/reference/skip.html) 


### Other environments

ami can be used to check any environment variable.
For example, we can see if we're running in a [Poetry](https://python-poetry.org) environment:

```{r}
ami::using_envvar("POETRY_ACTIVE")
```

We can also check for package options.
Here, we'll see whether [boot](https://cran.r-project.org/package=boot) is configured to do parallel bootstrapping using multiple cores:

```{r}
ami::using_option("boot.parallel", "multicore")
```

If you're using options as part of package development, check out the [options](https://cran.r-project.org/package=options) package.


